Austraits – a curated plant trait database for the Australian flora

### 2018-07-07 ms.Rmd
Some relevant references

- traits now widely agreed as important [@westoby2002]
-	Legacy data vs. newly-collected traits  considerations for these differ and Austraits can offer a path for how to sample comprehensively
-	Web portal, maybe like coral traits, for easily adding new data which can accommodate a range of user’s capabilities
-	Family level plotting for the paper, featuring two traits – continuous and categorical  height and growth form; two important traits which we have good coverage for
-	CURATED national collection of traits, similar to other biodiversity datasets 
-	Expose decisions which are being made in the processing of data into a harmonised resource with a view to nationalising the availability of trait information, similar to availability similar to the availability of species occurrence data
-	What can a national dataset facilitate? Alignment with conservation management across a federlaised system of government. Global platforms might be best built from national datasets (analogous to the GBIF initiative which aggregates occurrence data assembled by national initiatives). 
-	Current models of trait aggregation are geographically patchy – with some locations comprehensively covered e.g. Europe – but with little taxonomic or functional overlap with other regions (e.g. Africa, Australia). ~5% of the worlds plant species occur in these regions (300 trees in Europe 600 in America; in a single 50-ha plot in Australian tropical forests = same or more species). This actually matters when we increasingly want to apply traits as a proxy for understanding vegetation responses to disturbance and change. Whilst large-scale analyses are relatively well-served by global datasets which have representatives species from each biome or continent, the capacity to explore more nuanced questions about the function of regional vegetation is limited. 
-	Duplication of effort. Austraits will reduce the duplication of effort across government research agencies and university researchers seeking to create trait-based approaches to their questions. 
-	Better stewardship of data when collected by a localised group of interested parties.

@@

The data are housed within github repository traitecoevo with sequential releases being made available on this platform and Zenodo/Figshare. Access to Austraits will be  XXX. Austraits can also be accessed via the R package: `austraits`

@@

Austraits is designed to collate traits-based measurements with a range of relevant contextual information. Its schema broadly follows the principles of the established Observation and Measurement Ontology (Madin et al., 2007) in that trait data are connected to contextual information. Data flows from individual ‘studies’ which are any natural grouping for data collections, typically scientific publications, species descriptions, and field campaigns. Austraits currently contains X studies and each study has two associated files: `data.csv` and `metadata.yml`. `Metadata.yml` must conform to a standard set of fields to provide context and options for converting data into standardised format via information on trait-mapping.

>>>>

- traits now widely agreed as important [@Westoby-2002]
-	Legacy data vs. newly-collected traits  considerations for these differ and Austraits can offer a path for how to sample comprehensively
-	Web portal, maybe like coral traits [@Madin-2016], for easily adding new data which can accommodate a range of user’s capabilities
-	Family level plotting for the paper, featuring two traits – continuous and categorical  height and growth form; two important traits which we have good coverage for
-	CURATED national collection of traits, similar to other biodiversity datasets 
-	Expose decisions which are being made in the processing of data into a harmonised resource with a view to nationalising the availability of trait information, similar to availability similar to the availability of species occurrence data
-	What can a national dataset facilitate? Alignment with conservation management across a federlaised system of government. Global platforms might be best built from national datasets (analogous to the GBIF initiative which aggregates occurrence data assembled by national initiatives). 
-	Current models of trait aggregation are geographically patchy – with some locations comprehensively covered e.g. Europe – but with little taxonomic or functional overlap with other regions (e.g. Africa, Australia). ~5% of the worlds plant species occur in these regions (300 trees in Europe 600 in America; in a single 50-ha plot in Australian tropical forests = same or more species). This actually matters when we increasingly want to apply traits as a proxy for understanding vegetation responses to disturbance and change. Whilst large-scale analyses are relatively well-served by global datasets which have representatives species from each biome or continent, the capacity to explore more nuanced questions about the function of regional vegetation is limited. 
-	Duplication of effort. Austraits will reduce the duplication of effort across government research agencies and university researchers seeking to create trait-based approaches to their questions. 
-	Better stewardship of data when collected by a localised group of interested parties.

@@

The data are housed within github repository traitecoevo with sequential releases being made available on this platform and Zenodo/Figshare. Access to Austraits will be  XXX. Austraits can also be accessed via the R package: `austraits` Releases versioned, following [@Falster-2017]

@@

Austraits is designed to collate traits-based measurements with a range of relevant contextual information. Its schema broadly follows the principles of the established Observation and Measurement Ontology [@Madin-2007] in that trait data are connected to contextual information. Data flows from individual ‘studies’ which are any natural grouping for data collections, typically scientific publications, species descriptions, and field campaigns. Austraits currently contains X studies and each study has two associated files: `data.csv` and `metadata.yml`. `Metadata.yml` must conform to a standard set of fields to provide context and options for converting data into standardised format via information on trait-mapping.
